PANCHANGE_analysis

### 2020-08-26 PANCHANGE_analysis.Rmd
added correlation matrix for disorders

Load packages
```{r Load packages}
library(knitr)
library(summarytools)
library(psych)
library(patchwork)
library(broom)
library(tidyverse)
```

@@

>>>>

Load packages
```{r Load packages}
library(knitr)
library(summarytools)
library(psych)
library(polycor)
library(corrplot)
library(patchwork)
library(broom)
library(tidyverse)
```

@@

Correlation matrix of psychiatric disorders
```{r Correlation matrix of psychiatric disorders}
# Select items for correlation matrix
mhd.items <- c(
    "depressive_disorders",
    "anxiety_disorders",
    "eating_disorders",
    "obsessive_compulsive_disorders",
    "psychotic_disorders",
    "mhd.mania_hypomania_bipolar_or_manicdepression",
    "mhd.posttraumatic_stress_disorder_ptsd",
    "autism_spectrum_disorder",
    "mhd.attention_deficit_hyperactivity_disorder",
    "mhd.personality_disorder",
    "control"
)

# Calculate correlation matrix on specific columns (variables) from your data frame
mhd.corr.mat <- hetcor(
  as.data.frame(dat[,mhd.items]), # Specify the data
  use = "pairwise.complete.obs" # Use all pairwise observations
)

# Print the correlation matrix
print(mhd.corr.mat, digits = max(3, getOption("digits") - 3))

# Save the correlations from the correlation matrix in an object
mhd.corr.matrix <- as.matrix(mhd.corr.mat)

# Save the p values from the correlation matrix in an object
mhd.p.matrix <- as.matrix(mhd.corr.mat$tests)
```

Create the correlation matrix plot using the corrplot package
```{r Correlation matrix of psychiatric disorders plot, fig.height=7}
corrplot(mhd.corr.matrix, 
         method = "color", # objects to represent the correlations on plot
         type = "lower", # only use the lower triangle of the matrix
         diag = FALSE, # do not show the correlations on the diagonal
         addgrid.col = NA,
         addCoef.col = "black", # colour for the correlation coefficients in the plot
         tl.cex = 0.8,
         tl.col = "black",
         col=colorRampPalette(c("dodgerblue4","white","firebrick4"))(200), # colours for correlations
         # Combine with significance
         p.mat = mhd.p.matrix, # Matrix with p values
         sig.level = 0.01, # Choose significant level
         insig = "blank" # Nonsignificant correlations have no colour
         )
```
